\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{Xenara AI \\ NestJS Backend Intern}

\opening{Dear Hiring Team,}

I am excited to apply for the NestJS Backend Intern position at Xenara AI. With hands-on experience developing and deploying full-stack web applications, I am eager to contribute to your mission of redefining customer support through innovative AI solutions.

In my development journey, I’ve built three professional websites that showcase my ability to design and implement scalable, high-performance APIs:
\begin{itemize}
    \item \textbf{machinetelevision.com}: A web store for a skate brand, integrating Stripe for secure transactions, built with Next.js, PostgreSQL, and Tailwind CSS.
    \item \textbf{joaquinmoralesdp.com}: A portfolio site for a cinematographer, optimized for fast loading and responsive design using Next.js and Tailwind CSS.
    \item \textbf{greasyvocab.com}: A full-stack application for GRE flashcard generation, leveraging OpenAI’s API and incorporating PayPal for donations.
\end{itemize}

These projects honed my skills in JavaScript, TypeScript, and Node.js, along with proficiency in database management and API integration. My familiarity with Git version control and eagerness to learn new frameworks like NestJS align with the technical requirements of this internship.

I am particularly drawn to Xenara AI’s emphasis on innovation and teamwork. Collaborating on cutting-edge solutions like Pinecone DB integration and optimizing MongoDB queries excites me, as does the chance to develop within a supportive environment where growth is valued. I thrive in fast-paced settings and am confident my adaptability and problem-solving abilities will contribute to your goals.

Thank you for considering my application. I look forward to the opportunity to bring my technical expertise, curiosity, and collaborative spirit to Xenara AI.

\vspace{1em}


Sincerely, \\ 
Ricky Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}