\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{
A24 \\
New York, NY}

\opening{Dear Hiring Manager,}

“HAAARK! Hark, Triton, hark!” The cries from \emph{The Lighthouse} echo in my mind whenever I think about the epic that makes filmmaking possible. Lights hum, cameras whirl, servers buzz—every piece working in concert to bring stories to life. Just as Willem Dafoe’s keeper maintained the towering beacon in isolation, unseen but essential, IT ensures that the teams behind production and distribution never falter. That’s the work I want to do at A24.

Technology has always been a part of my life. My father ran an IT consultancy, and I grew up surrounded by machines—not just using them, but taking them apart, learning how to put them back together, and making them do cool stuff. Later, at Kenyon College, I studied Film while working as an IT Assistant, troubleshooting hardware and software across campus. Whether repairing workstations, assisting faculty with email configurations, or resolving networking issues, I focused on making technology seamless. 

Beyond IT support, my experience extends to high-stakes, high-collaboration environments. On student film sets, I learned how to work under pressure, adjust to last-minute changes, and communicate clearly across departments. Recently, I helped oversee the national BDPA High School Coding Competition, providing IT support by setting up testing environments, managing GitHub submissions, and ensuring a fair, secure competition. These experiences have shaped my ability to stay patient, precise, and adaptable—whether working with creatives on a film or engineers on an infrastructure issue.

A24 has redefined modern independent cinema, and I want to contribute to that legacy. I take pride in my ability to solve problems, explain technology in a way that makes sense to all users, and ensure that systems function as reliably as the stories they support. I look forward to the opportunity to bring my skills, passion, and dedication to your IT team.

\closing{Sincerely,}

Richard A. Alvarez \\
+1 (773) 469-9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois (Relocating to New York)

\end{letter}


\end{document}