%-------------------------
% Resume in Latex
% Author : Aras Gungore
% Edits: Richard A. Alvarez
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome5}
\usepackage{iftex}
\usepackage{fontspec}
\usepackage{xspace} 

\setmainfont{Avenir}

\frenchspacing 

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter} 

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable

%-------------------------
% Custom commands

\newcommand{\xsmall}{\fontsize{8pt}{8pt}\selectfont}
\newcommand{\normal}{\fontsize{16pt}{16pt}\selectfont}
\newcommand{\titlef}{\fontsize{21pt}{21pt}\selectfont}

\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

% Footer
\fancypagestyle{firstpage}{
  \fancyhf{} % clear all header and footer fields
}

\fancypagestyle{otherpages}{
  \fancyhf{} % clear all header and footer fields
  \fancyfoot[C]{\small Richard Álvarez | 2024}
}

\pagestyle{otherpages}
\thispagestyle{firstpage}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[6]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
		\textit{\small#5} & \textit{\small #6} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & #2 \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & {\small #2} \\
		\textit{\small#3}
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSmallOrganizationHeading}[4]{
	\small{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & {\small #2} \\
		\textit{\small#3} & \textit{\small #4} 
	\end{tabular*}\vspace{-7pt}
	}
}

\newcommand{\resumeCert}[3]{
	\small{
	\vspace{-4pt}\item
	\textbf{#1} {\textit{\small #2}} \\
	\xsmall{#3}  % Small text for keywords
	}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeParagraph}[1]{
	\item[]
	\parbox{\linewidth}{
		\small{#1\xspace} % Modify this line
	}
	\vspace{-7pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
	\textbf{\titlef \scshape Richard Álvarez} \\ \vspace{3pt}
	\vspace{8pt}
	\small
	\hspace{.5pt} \href{mailto:rawalvarez731@gmail.com}{rawalvarez731@gmail.com} \hspace{.5pt}
	$/$
	 \hspace{.5pt} \href{https://github.com/raulduk3}{GitHub} \hspace{.5pt}
	$/$
	\hspace{.5pt} \href{https://raulduke.com}{raulduke.com} \hspace{.5pt}
	$/$
	\hspace{.5pt} Relocating to Brooklyn, NY
\end{center}

%----------- ABOUT ME  -----------

\vspace{-8pt}

\section{About Me}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeParagraph{Aspiring IT professional skilled in troubleshooting, user training, and maintaining technology systems. Experienced in optimizing workflows and delivering high-quality customer service. Passionate about empowering communities through technology, with a strong foundation in video production, programming, and technical problem-solving.}


\vspace{2pt}

\resumeSubHeadingListEnd

\vspace{-12pt}

%----------- EDUCATION -----------

\section{Education}
\vspace{4pt}
\resumeSubHeadingListStart

\resumeEducationHeading
{New York University (NYU) Tandon School of Engineering}{Brooklyn, New York}
{Master of Science in Computer Engineering}{Aug 2025 (Expected)}{}
{}{}
\vspace{-8pt}

\resumeEducationHeading
{Kenyon College}{Gambier, Ohio}
{Bachelor of Arts in Film; GPA: 3.4/4.0}{Aug 2020 – May 2024}
{Minor in History and Concentration in Integrated Program in Humane Studies}{}
\resumeParagraph{Authored two papers on machine learning applications in creative industries. Produced and edited over 15 experimental video projects, including music videos, audio-reactive visualizations, and short films.}

\resumeParagraph{Relevant coursework includes AI for the Humanities (IPHS 300), Advanced Post-Production (FILM 391), Data Structures and Program Design (SCMP 218), Digital Photography (ARTS 321), Sex, Drugs, Guns: Research Strategies in the Contemporary Age (INDS 140), and Software Development (SCMP 318).}

%----------- Archived  -----------

\iffalse
\resumeSubheading
{Walter Payton College Preparatory 
% \normalfont{(Admission rate: 0.85\%)}
}{Chicago, Illinois}
{High School Diploma}{Sep 2016 \textbf{--} Jun 2020}
\fi

\resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Work Experience}
\vspace{4pt}
\resumeSubHeadingListStart

\resumeSubheading
{IT Assistant}{Gambier, Ohio}
{Library and Information Services (LBIS), Kenyon College · Part-time}{Sep 2023 – Feb 2024}
\resumeParagraph{Provided front-line IT support to students and faculty, troubleshooting hardware and software issues across Windows and macOS systems. Managed ServiceNow tickets, ensuring timely resolutions. Assisted with classroom technology setup, printer maintenance, and peripheral configurations. Delivered remote support via remote-in tools and performed basic networking diagnostics.}

\vspace{2pt}

\resumeSubheading
{LEGO STEM Instructor}{Chicago, Illinois}
{Play-Well TEKnologies · Part-time}{Oct 2024 – Dec 2024}
\resumeParagraph{Taught STEM-focused LEGO engineering classes, introducing mechanical and programming concepts to children. Adapted instruction to various learning styles and managed class engagement. Communicated effectively with parents and staff to ensure a structured learning environment.}

\vspace{2pt}

\resumeSubheading
{Script Reader}{Columbus, Ohio}
{Good Deed Entertainment · Internship}{May 2022 – June 2022}
\resumeParagraph{Analyzed incoming screenplay submissions, evaluating narrative structure, character development, and commercial viability. Wrote detailed coverage reports summarizing strengths, weaknesses, and recommendations for acquisitions. Provided insights on potential projects, aligning with the company’s content strategy.}

\vspace{2pt}

\resumeSubheading
{Research Assistant}{Chicago, Illinois}
{University of Chicago · Part-time}{Aug 2018 - Nov 2019}
\resumeParagraph{Worked under Bernard Dickens III on an academic paper focused on cybersecurity and supply-chain attacks. Contributed 27 commits to repository code reviews. Explored cryptographic checksum verification methods to detect unauthorized software modifications.}

%———– Archived  ———–
\iffalse

\resumeSubheading
{Fontanos Subs}{Chicago, Illinois}
{Sub Artist · Part-time}{May 2021 – Aug 2021}
\resumeParagraph{Worked behind the counter making sandwiches, maintaining cleanliness, and ensuring efficient service. Assisted with troubleshooting online orders, ensuring customer satisfaction and smooth operations.}

\resumeSubheading
{Private Stock Studios}{Chicago, Illinois}
{Production Assistant}{Apr 2020 – Aug 2020}
\resumeParagraph{Streamlined film and music production processes, orchestrated schedules with studio professionals, and meticulously documented production details.}

\resumeSubheading
{Intercultural Montessori}{Chicago, Illinois}
{Teacher’s Aid}{Apr 2019 – Feb 2020}
\resumeParagraph{Tutored students, facilitated programming learning, provided teacher support, and ensured effective communication and punctuality.}

\fi

\resumeSubHeadingListEnd

%———– CERTIFICATES ———–
% \iffalse
\section{Certificates}
\vspace{6pt}
\resumeSubHeadingListStart

\resumeCert{CompTIA ITF+}{Sep 2024}{IT fundamentals, troubleshooting, hardware, networking basics}

\resumeCert{NYU Tandon Bridge}{Mar 2025}{Discrete mathematics, data structures, algorithms, C++ programming}

\resumeSubHeadingListEnd
% \fi

%----------- SKILLS -----------
\section{Skills}
\resumeSubHeadingListStart
\small{\item{
\textbf{Technical Support}: Windows/macOS troubleshooting, software and hardware installation, remote support, user training, ticket management \\ \vspace{2pt}
\textbf{Networking}: VPN setup, basic network configuration, security monitoring, device provisioning \\ \vspace{2pt}
\textbf{Cloud \& Security}: Office 365, Google Workspace, secure file handling, endpoint security, password management \\ \vspace{2pt}
\textbf{IT Operations}: Asset management, system imaging, hardware deployment, IT project support \\ \vspace{2pt}
\textbf{Soft Skills}: Customer service, documentation, troubleshooting, teamwork, problem-solving \\ \vspace{2pt}
}}
\resumeSubHeadingListEnd


\end{document}
