\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{Zoro \\
Chicago, IL}

\opening{Dear Hiring Staff,}

I am excited to apply for the Desktop Support Technician position at Zoro. With my background in IT support and hands-on experience with troubleshooting hardware and software issues, I am eager to contribute to your team. Zoro’s commitment to providing essential tools for business owners and its inclusive culture aligns with my professional values and aspirations.

In my role as an IT Assistant at Kenyon College, I supported campus-wide technology needs by preparing workstations, managing operating system installations, and securely handling data. I utilized ticketing systems to track and resolve incidents, ensuring minimal downtime and optimal performance. My ability to diagnose and resolve technical issues promptly has been honed through real-world experience and a proactive approach to problem-solving.

My academic background in Film, combined with a minor in History and a concentration in Integrated Program in Humane Studies, has equipped me with strong analytical and critical thinking skills. These skills are essential for developing long-term strategies and capacity planning for meeting future organizational hardware needs, as mentioned in the job description.

I am particularly drawn to Zoro’s innovative approach and dedication to fostering an inclusive work environment. My hands-on experience with PC and Mac hardware, along with my proficiency in managing peripheral devices and providing end-user assistance, make me a strong candidate for this role. I am confident in my ability to collaborate effectively with IT team members to ensure the efficient operation of Zoro’s computing environment.

Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and enthusiasm can contribute to the success of Zoro. 

\vspace{1em}

Sincerely, \\ 
Richard A. Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}