\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{
Fusion Education \\
935 57th St \\
Brooklyn, NY 11219}

\opening{Dear Hiring Manager,}

I am excited to apply for the Coding Instructor position at Fusion Education. With a background in programming, digital humanities, and mentoring, I am eager to bring my technical skills and passion for education to your team. My experience working with students and my proficiency in Python and Scratch make me well-suited for this role.

As a researcher and developer with experience in Python and JavaScript, I have built projects that integrate machine learning, creative computing, and data visualization. At Kenyon College, I explored AI applications in the humanities, producing projects that combined programming with storytelling and analysis. Additionally, I have mentored students in coding and problem-solving through my involvement with the Black Data Processing Associates (BDPA), where I served as a national coding competition judge and mentor.

Key qualifications that align with this role include:
\begin{itemize}
    \item Proficiency in Python and Scratch, with experience developing interactive and educational coding projects.
    \item Experience mentoring and teaching students in coding fundamentals and problem-solving strategies.
    \item Strong communication skills to engage and guide young learners effectively.
    \item Commitment to completing a full course term and fostering a positive learning environment.
    \item Passion for STEM education and hands-on learning, including experience with robotics and digital creativity.
\end{itemize}

I am particularly drawn to this opportunity at Fusion Education because of its focus on empowering young learners through coding and robotics. I look forward to the opportunity to further discuss how my skills and enthusiasm for education can contribute to your team.

\closing{Sincerely,}

Richard A. Alvarez \\
+1 (773) 469-9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois (Open to Relocation)

\end{letter}
\end{document}
