\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{
CyberCoders \\
New York, NY}

\opening{Dear Hiring Manager,}

Technology should make life easier, not more frustrating. That belief has guided me throughout my experience in IT support, from helping faculty and students troubleshoot systems at Kenyon College to developing automation tools that streamlined maintenance workflows. As I prepare to move to New York for graduate studies at NYU Tandon, I am eager to bring my problem-solving skills and customer-first mindset to your team as an IT Support Associate.  

In my role as an IT Assistant at Kenyon’s Library and Information Services, I provided hands-on technical support across campus, resolving hardware and software issues, managing user accounts, and maintaining IT assets. I worked within a ticketing system to track and prioritize requests, ensuring efficient resolutions while delivering clear, patient communication. Additionally, I developed a scheduling tool that optimized classroom technology maintenance, reducing downtime and improving service delivery.  

Beyond troubleshooting, I understand that IT is ultimately about people—ensuring they have the tools they need to do their jobs without disruption. I take pride in translating technical issues into clear solutions, whether that means walking a user through a fix remotely or collaborating with a team to improve IT processes. My familiarity with ticketing systems, remote support tools, and IT documentation practices makes me confident that I can contribute immediately to your support operations.  

New York is a city built on speed and efficiency, and I’m excited to apply that same energy to solving IT challenges. I welcome the opportunity to discuss how my experience and enthusiasm can support your team’s mission.  

\closing{Best regards,}

Richard A. Alvarez \\
+1 (773) 469-9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois (Open to Relocation)

\end{letter}
\end{document}
