\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{SITU Fabrication \\
63 Flushing Ave, Bldg 132 \\
Brooklyn, New York 11205}

\opening{Dear Hiring Team,}

Hey all, my name is Rick Alvarez, and I am a native born Chicagoan who is moving to Brooklyn for my post-graduate education! I am super excited to apply for the Shop Associate position at SITU Fabrication. Your commitment to innovative design, experimental techniques, and interdisciplinary collaboration is inspiring, and I am eager to contribute to the work happening at your Brooklyn Navy Yard facility. As someone who thrives in hands-on, team-oriented environments, I look forward to supporting your fabrication process while growing with your organization.

In my role as an IT Assistant at Kenyon College, I developed skills in equipment maintenance, inventory management, and optimizing workflows through technical solutions. For example, I implemented a digital scheduling system that streamlined classroom maintenance and resource allocation. At Sommerlad Construction, I honed my ability to work with a wide range of power tools, meet daily deadlines, and handle physically demanding tasks such as material transport and demolition. These experiences taught me the importance of precision, adaptability, and communication—values that resonate with SITU Fabrication’s approach.

I am particularly drawn to SITU’s ability to merge advanced fabrication technologies, like 3D modeling and parametric tools, with creative problem-solving. My long-term goal is to advance into roles that integrate computational tools and research to contribute to complex, experimental projects. Joining SITU now as a Shop Associate would allow me to support your production efforts while continuing to build the skills necessary to thrive in your interdisciplinary environment.

Thank you for considering my application. I would love the opportunity to discuss how my technical expertise, physical capabilities, and passion for innovative design align with SITU Fabrication’s needs. I am available at your convenience and look forward to the chance to contribute to your exciting projects.

\vspace{1em}

Sincerely, \\
Richard (Rick) Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}
