%-------------------------
% Resume in Latex
% Author : Aras Gungore
% Edits: Richard A. Alvarez
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome5}
\usepackage{iftex}
\usepackage{fontspec}
\usepackage{xspace} 

\setmainfont{Avenir}

\frenchspacing 

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter} 

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable

%-------------------------
% Custom commands

\newcommand{\xsmall}{\fontsize{8pt}{8pt}\selectfont}
\newcommand{\normal}{\fontsize{16pt}{16pt}\selectfont}

\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

% Footer
\fancypagestyle{firstpage}{
  \fancyhf{} % clear all header and footer fields
}

\fancypagestyle{otherpages}{
  \fancyhf{} % clear all header and footer fields
  \fancyfoot[C]{\small Richard Álvarez | 2024}
}

\pagestyle{otherpages}
\thispagestyle{firstpage}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[6]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
		\textit{\small#5} & \textit{\small #6} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & #2 \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{\small #2} \\
		\textit{\small#3}
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeCert}[2]{
	\small{
	\vspace{-4pt}\item
	\textbf{#1} {\textit{\small #2}}
	}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeParagraph}[1]{
	\item[]
	\parbox{\linewidth}{
		\small{#1\xspace} % Modify this line
	}
	\vspace{-7pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
	\textbf{\normal \scshape Richard Álvarez} \\ \vspace{3pt}
	\vspace{12pt}
	\small
	\faMobile \hspace{.5pt} \href{tel:7734699726}{+1 773 469 9726}
	$|$
	\faAt \hspace{.5pt} \href{mailto:rawalvarez731@gmail.com}{rawalvarez731@gmail.com}
	$|$
	\faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Chicago,+IL/@41.833871,-87.8967704,11z/data=!3m1!4b1!4m6!3m5!1s0x880e2c3cd0f4cbed:0xafe0a6ad09c0c000!8m2!3d41.8781136!4d-87.6297982!16zL20vMDFfZDQ?entry=ttu}{Chicago, Illinois}
\end{center}

%----------- ABOUT ME  -----------

\section{About Me}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeParagraph{
I am a dedicated and adaptable professional with a passion for hands-on work and collaborative problem-solving. My background includes experience in IT support and construction, where I developed skills in equipment maintenance, material handling, and workflow optimization. I thrive in fast-paced environments that require attention to detail and teamwork. I am excited to contribute to SITU Fabrication’s mission by supporting production and shop improvement efforts, and I am eager to grow within the company as I begin my postgraduate studies in Computer Engineering at NYU Tandon.
}

\resumeSubHeadingListEnd

\vspace{-12pt}

%----------- EDUCATION -----------

\section{Education}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeEducationHeading
{New York University (NYU) Tandon School of Engineering}{Brooklyn, New York}
{Master of Science in Computer Engineering}{Aug 2025}{}
{}{}
\vspace{-8pt}

\resumeEducationHeading
{Kenyon College}{Gambier, Ohio}
{Bachelor of Arts in Film; GPA: 3.47/4.00}{Aug 2020 - May 2024}
{Minor in History and Concentration in Integrated Program in Humane Studies}{}
\vspace{-1pt}
\resumeItemListStart
\resumeItem{\textbf{Relevant coursework:} {Senior Research Seminar, AI for the Humanities, Software Development, Programming Humanity, Data Structures \& Program Design, Introduction to Programming}}
\resumeItem{\textbf{Extracurriculars:} {Horn Gallery Videographer, Club Basketball, KSJP}}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Work Experience}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeSubheading
{Library and Information Services (LBIS), Kenyon College}{Gambier, Ohio}
{IT Assistant}{Sep 2023 - Feb 2024}
\resumeParagraph{I supported campus-wide technology needs by preparing workstations, moving office tech, and securely erasing and recycling equipment. I restocked printers daily. I demolished hard drives. I conducted classroom checks under the guidance of team members.  I streamlined team projects by applying programming skills, in one instance by generating a spreadsheet of course meetings and classroom locations to determine when our techs could perform maintenance.}

\vspace{2pt}

\resumeSubheading
{Sommerlad Construction}{Chicago, Illinois}
{General Contractor}{Jun 2023 - Aug 2023}
\resumeParagraph{I participated in demolition projects for remodeling efforts, performed general land management tasks such as lawn mowing and simple assembly, and supported the team in meeting deadlines and adhering to safety standards.}

\resumeSubheading
{Fontanos Subs}{Chicago, Illinois}
{Sub Artist}{May 2021 – Aug 2021}
\resumeParagraph{Worked behind the counter making sandwiches, maintaining cleanliness, and ensuring efficient service. Assisted with troubleshooting online orders, ensuring customer satisfaction and smooth operations.}


%———– Archived  ———–

\iffalse
	\resumeSubheading
	{Private Stock Studios}{Chicago, Illinois}
	{Production Assistant}{Apr 2020 \textbf{–} Aug 2020}
	\resumeParagraph{Streamlined film and music production processes, orchestrated schedules with studio professionals, and meticulously documented production details.}

	\resumeSubheading
	{Intercultural Montessori}{Chicago, Illinois}
	{Teacher’s Aid}{Apr 2019 \textbf{–} March 2020}
	\resumeParagraph{Tutored students, facilitated programming learning, provided teacher support, and ensured effective communication and punctuality.}
\fi


%———– RESEARCH EXPERIENCE ———–

%\section{Research Experience}
%  \vspace{3pt}
%  \resumeSubHeadingListStart

%  \resumeSubHeadingListEnd

%———– AWARDS & ACHIEVEMENTS ———–

%\section{Awards & Achievements}
%  \vspace{2pt}
%  \resumeSubHeadingListStart
%    \small{\item{
%   		\textbf{High Honors Degree:}{ Awarded to Bachelor alumni who have graduated with a GPA greater than or equal to 3.50 by Boğaziçi University.} \ \vspace{3pt}
%
%    }}
%  \resumeSubHeadingListEnd\textsl{•}

%———– PUBLICATIONS ———–

\section{Publications}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{A Retrieval-Augmented Film Recommendation System} $|$ \emph{\href{https://github.com/raulduk3/language-model-driven-film-recommendation}{\color{blue}GitHub}} $|$ \emph{\href{https://digital.kenyon.edu/dh_iphs_ss/34/}{\color{blue}Digital Kenyon}} $|$ \xsmall{May 2024}}{}
\resumeItemListStart
\resumeItem{Utilized LangChain’s OpenAI integration for dynamic query generation based on user preferences, demonstrating the potential for generative AI techniques in digital entertainment.}
\resumeItem{Developed a Retrieval-Augmented Film Recommendation System using Node.js, integrating OMDb and TMDb APIs to enhance movie metadata for precise and personalized recommendations.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Unsupervised Deep Learning and PySceneDetect Analysis} $|$ \emph{\href{https://github.com/raulduk3/pySceneDetect-video-editing-trends}{\color{blue}GitHub}} $|$ \emph{\href{https://digital.kenyon.edu/dh_iphs_ss/22/}{\color{blue}Digital Kenyon}} $|$ \xsmall{May 2023}}{}
\resumeItemListStart
\resumeItem{Analyzed short-format video editing trends using PySceneDetect and DNNs.}
\resumeItem{Employed t-SNE and PCA for data visualization and pattern discovery.}
\resumeItemListEnd

%———– Archived  ———–

\iffalse
	\resumeProjectHeading
	{\textbf{AI-Driven Kubrick-Inspired Film Script Generation} $|$ \emph{\href{https://github.com/raulduk3/kubrick-gen}{\color{blue}GitHub}}}{}
	\resumeItemListStart
	\resumeItem{Created an AI pipeline for generating film scripts inspired by Stanley Kubrick’s style.}
	\resumeItem{Designed an API using Dust.tt for script generation with Large Language Models.}
	\resumeItemListEnd
	
\resumeSubHeadingListEnd

%———– SKILLS ———–

\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
\textbf{Hands-On Skills:} Material handling, equipment maintenance, power tools, hand tools \\ \vspace{2pt}
\textbf{Physical Abilities:} Lifting and moving up to 50 lbs, extended periods of standing \\ \vspace{2pt}
\textbf{Technical Skills:} Python, JavaScript/Typescript, SQL, inventory management systems \\ \vspace{2pt}
\textbf{Applications:} DaVinci Resolve, Adobe Suite, CAD (basic), Cinema4D \\ \vspace{2pt}
\textbf{Languages:} English (Fluent), Spanish (Intermediate) \\ \vspace{2pt}
}}
\resumeSubHeadingListEnd


%———– CERTIFICATES ———–

\section{Certificates}
\vspace{6pt}
\resumeSubHeadingListStart

\resumeCert{CompTIA ITF+}{Sep 2024}

\resumeCert{NYU Tandon Bridge}{Mar 2025}

\resumeSubHeadingListEnd


%----------- REFERENCES -----------	
\section{References}
\vspace{2pt}
\resumeSubHeadingListStart

\item{
\textbf{Steve Krajenski} \\ 
{ IT Supervisor, Kenyon College \\  
\href{mailto:krajenski1@kenyon.edu}{krajenski1@kenyon.edu}} \\
(740) 504-0328 \\
}
\item{
\textbf{Bernard Dickens III} \\ 
{ CTO, Ergodark LLC \\ 
\href{mailto:me@bernarddickens.com}{me@bernarddickens.com}} \\
}
\item{
\textbf{Jon Chun} \\ 
{ Visiting Instructor, Kenyon College \\  
\href{mailto:chunj@kenyon.edu}{chunj@kenyon.edu}} \\
}

\resumeSubHeadingListEnd

%————— END ————————––

\end{document}