\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{THC by Chitiva \\
1250 S Michigan Ave. \\
Chicago, IL 60622}

\opening{Dear Hiring Team,}

I am writing to express my enthusiasm for the Retail Sales Assistant position at THC by Chitiva. Although I do not have direct experience in the cannabis industry, I am eager to learn and am fully committed to obtaining any necessary certifications, such as the Food Handler Certification, to ensure I can contribute effectively to your team.

My background in customer service, retail operations, and technology support has provided me with the skills needed to excel in this role. At Fontanos Subs, I worked behind the counter preparing sandwiches, maintaining a clean and organized workspace, and assisting customers with online orders. This experience has honed my ability to work efficiently in fast-paced environments while delivering exceptional service.

In addition to my retail experience, I have a strong foundation in IT and technology support from my role as an IT Assistant at Kenyon College. This has equipped me with problem-solving skills, attention to detail, and the ability to troubleshoot and resolve issues—abilities that I am confident will translate well to the cannabis retail industry.

I am particularly drawn to THC by Chitiva because of your commitment to providing top-tier products and a unique customer experience. The opportunity to be part of a team that is passionate about the cannabis industry and dedicated to customer satisfaction is incredibly appealing. I am excited about the prospect of growing with your company and contributing to the dynamic environment that THC by Chitiva offers.

Thank you for considering my application. I am eager to bring my strong work ethic, adaptability, and enthusiasm to your team. I look forward to the possibility of discussing how my background, combined with my willingness to obtain the required certifications, can contribute to the success of THC by Chitiva.

\vspace{1em}

Sincerely, \\
Richard A. Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}