\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{Old Mission \\
Chicago, IL 60654}

\opening{Dear Hiring Team,}

I am excited to apply for the Junior Software Engineer position at Old Mission. With a strong foundation in web development, systems programming, and a passion for learning about trading technologies, I believe I can make an immediate impact on your team.

Over the past several years, I have built more than five professional full-stack web applications as a freelance developer, utilizing technologies like React, Node.js, and SQL. My technical background also includes developing three C++ projects available on my GitHub, demonstrating my ability to write and debug memory efficient code. These projects honed my understanding of data structures, algorithms, and systems programming, all of which are critical for supporting C++-based trading applications.

I am proficient in Linux and advanced development environments, which has allowed me to troubleshoot complex systems and streamline deployments. My academic background, including coursework in Data Structures, Software Development, and AI for the Humanities, complements my practical experience and prepares me for the analytical challenges of electronic trading.

I am particularly intrigued by the opportunity to contribute to Old Mission’s creative programming initiatives. The prospect of supporting real-time trading operations while expanding my knowledge of trading systems excites me. I am eager to grow my understanding of how C++ and Python drive performance in trading environments.

Thank you for considering my application. I look forward to the opportunity to bring my technical expertise, curiosity, and strong work ethic to Old Mission.

\vspace{1em}

Sincerely, \\ 
Ricky Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}