\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{Northwestern University \\
IT Media \& Tech Innovation Department \\
Chicago, IL}

\opening{Dear Hiring Staff,}

I am thrilled to apply for the position in IT Media \& Tech Innovation at Northwestern University. With a strong foundation in programming, problem-solving, and user support, I am excited about the opportunity to contribute to your team and support the university's technological advancements.

My experience as an IT Assistant at Kenyon College has equipped me with the skills necessary to excel in this role. I provided comprehensive support for campus-wide technology needs, including preparing workstations, managing equipment, and ensuring seamless classroom operations. My proactive approach to problem-solving and ability to streamline team projects using programming skills have been instrumental in achieving efficient outcomes. Developing documentation for support activities and ensuring problem resolution through diligent follow-ups have been key aspects of my role, aligning well with the responsibilities outlined in the job description.

In addition to my technical skills, my academic background in Film, with a minor in History and a concentration in the Integrated Program in Humane Studies, has honed my analytical and creative problem-solving abilities. These skills are essential for diagnosing issues, recommending application changes, and improving processes to increase efficiency and effectiveness. My involvement in various extracurricular activities, such as being a videographer for Horn Gallery and playing club basketball, has further developed my organizational and collaborative skills.

I am particularly drawn to this position at Northwestern University because of the institution's commitment to innovation and support for professional growth. The opportunity to work in an inclusive and dynamic environment, assisting with the development and maintenance of critical applications and services, is incredibly appealing. My hands-on experience with programming, project coordination, and user support, combined with my enthusiasm for continuous learning and improvement, make me a strong candidate for this role.

Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and passion can contribute to the success of the IT Media \& Tech Innovation Department at Northwestern University.

\vspace{1em}

Sincerely, \\ 
Richard A. Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}