\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

\frenchspacing{}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{SITU Research \\
Brooklyn Navy Yard \\
141 Flushing Ave \\
Building 77, Suite 508 \\
Brooklyn, NY 11205 }

\opening{Dear SITU Research Hiring Team,}

My name is Richard Alvarez, a Chicago-born researcher and web developer, and I am thrilled to apply for the Junior Computational Researcher position at SITU Research. As someone passionate about the intersection of technology, storytelling, and human rights, I am inspired by your commitment to using innovative visual tools to uncover and amplify critical truths.  

At Kenyon College, I earned a Bachelor’s degree in Film, with a minor in History and a concentration in Digital Humanities, exploring how computational methods can deepen storytelling. In courses like AI for the Humanities and Data Structures and Program Design, I honed my ability to analyze data and develop interactive visualizations. My academic projects included leveraging Python and metadata analysis to trace distinct editing styles across film genres.  

My filmmaking background has given me extensive experience with visual platforms and media of all types. From directing and editing experimental films to designing motion graphics in After Effects, I have cultivated a strong sense of visual storytelling. Additionally, I have created procedural animations and graphics in Cinema4D. This foundation in visual communication directly informs my ability to present complex ideas in accessible and compelling formats.  

I also have hands-on experience in open-source intelligence (OSINT), database research, metadata analysis, and social media monitoring. These skills were key in academic research projects emphasizing data verification and integrity. For instance, I designed and executed a sentiment analysis project by scraping user reviews from Rotten Tomatoes. Using Python libraries such as BeautifulSoup and NLTK, I extracted and processed reviews to analyze audience reactions and evaluate the reliability of the platform’s freshness ratings. This strengthened my ability to handle unstructured datasets and generate actionable insights.  

As a web programmer, I’ve built functional applications using frameworks like React and Next.js, integrated APIs, and optimized user experiences across platforms. I combine these technical skills with a focus on accessibility and design, producing tools that are both functional and user-friendly.  

Joining SITU Research represents an exciting opportunity to contribute to impactful, interdisciplinary projects while developing new skills in geospatial analysis, machine learning, and 3D reconstruction. As I begin my master’s program in Computer Engineering at NYU Tandon, I am eager to expand my technical expertise and use it to support SITU’s mission of amplifying truth through rigorous investigation.  

Thank you for considering my application. I would welcome the opportunity to discuss how my skills and experiences align with the Junior Computational Researcher role.  

\vspace{1em}

Sincerely, \\
Richard (Rick) Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}

\end{document}
