\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{University of Illinois Chicago's College of Liberal Arts \& Sciences \\
Chicago, IL}

\opening{Dear Hiring Staff,}
I hope this message finds you well. I am excited to apply for the Help Desk Support position in the College of Liberal Arts \& Sciences at UIC. With a strong background in IT support, a passion for liberal arts education, and being a local resident of Chicago, I am eager to contribute to the dynamic team at UIC and support the diverse needs of its students and staff.

As an IT Assistant at Kenyon College, I provided comprehensive technology support across campus, handling everything from troubleshooting hardware and software issues to streamlining maintenance processes. I generated detailed spreadsheets to improve tech maintenance schedules, managed operating systems installations, and ensured secure data handling. My experience using support tools like SCCM and Deploy Studio has equipped me with the skills needed to handle a variety of technical challenges efficiently.

I graduated from Kenyon College with a Bachelor of Arts in Film, a minor in History, and a concentration in the Integrated Program in Humane Studies. My academic journey in a liberal arts environment has instilled in me a deep appreciation for the diverse perspectives and critical thinking skills that such an education fosters. This background, combined with my technical expertise, positions me well to understand and meet the evolving needs of UIC’s College of Liberal Arts \& Sciences.

UIC’s commitment to providing a supportive and inclusive environment for its diverse student body aligns with my values. I am particularly impressed by UIC’s designation as a Minority Serving Institution and its efforts to support underrepresented communities. As a local resident of Chicago, I am excited about the opportunity to provide friendly and effective IT support, helping students and faculty navigate and utilize LAS systems and applications.

I am dedicated, hardworking, and committed to continuous improvement. My ability to diagnose and resolve technical issues, along with my excellent customer service skills, will allow me to contribute positively to the UIC community. I look forward to the opportunity to bring my experience and enthusiasm to the Help Desk Support role at UIC.

Thank you for considering my application. I am available for an interview at your earliest convenience and am excited about the possibility of joining the team at UIC.

\closing{Sincerely,}


Richard A. Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}
