\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{Smart Surfaces Coalition \\
Washington, DC}

\opening{Dear Mr. Berkowitz,}

I hope this message finds you well. I’m thrilled to apply for the Junior Software Developer position at Smart Surfaces Coalition (SSC). With a solid background in software development and a passion for social justice, I’m eager to contribute to SSC’s mission of creating sustainable urban environments.

In my role as an IT Assistant at Kenyon College, I tackled campus-wide technology needs, from troubleshooting issues to streamlining maintenance processes. I improved tech maintenance schedules by generating detailed spreadsheets and ran my own web services on AWS. With over five years of experience using Git, I’ve learned to manage code efficiently and collaborate seamlessly with teams.

Since high school, I’ve been building web-based applications, amassing years of research experience. I recently graduated from Kenyon College with a BA in Film, a minor in History, and a concentration in Integrated Program in Humane Studies. My coursework in Software Development, Data Structures \& Program Design, and AI for the Humanities laid a strong foundation in programming languages like Python, JavaScript, and SQL. One of my projects involved developing a full-stack web application using Next.js and large language models (LLMs) to create personalized GRE flashcards. This project demanded extensive data cleaning, processing, and unifying, all skills relevant to the tasks at SSC. Additionally, I’ve built applications using PostgreSQL, showcasing my ability to work with complex databases.

SSC’s work in promoting Smart Surfaces and addressing urban environmental justice is truly inspiring. I’m particularly excited about the opportunity to work with Clojure and ClojureScript and contribute to the Benefit-Cost Analysis Tool. A recent project of mine involved analyzing and displaying real solar panel data from schools in Guatemala, reflecting my dedication to using technology for social good. I’m eager to bring my web development, data analysis, and team collaboration skills to SSC.

I am confident that my software development background and commitment to social justice make me a great fit for this position. I look forward to discussing how my experiences and skills can contribute to the impactful work at SSC.

Thank you for considering my application. I’m available for an interview at your earliest convenience.

\closing{}


Sincerely,

Richard A. Alvarez \\
+1773 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}
