\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{Library and Information Services (LBIS) Team \\
Kenyon College \\
Chalmers Library, 3rd Floor \\
Gambier, Ohio}

\opening{Dear Hiring Committee,}

I am writing to express my enthusiasm for the IT Assistant position (SI9422) at Kenyon College for the 2023-2024 academic year. As a Bachelor of Arts in Film at Kenyon, concentrating on Computing and Integrated Program in Humane Studies, I am deeply committed to enhancing my technological expertise and contributing positively to the Kenyon community. 

My academic background has been rooted in computing and technology. With relevant coursework in Software Development, Data Structures and Program Design, and hands-on experience in programming languages like C, C++, Python, JavaScript, and Rust, I am well-equipped to tackle various technology-related tasks. My research experience in designing and implementing novel web browser extensions and my projects on Deep Learning and AI-driven script generation showcase my ability to adapt to new technologies and work collaboratively on innovative solutions.

In my previous work experience at Sommerlad Construction and Private Stock Studios, I have demonstrated a strong aptitude for teamwork, efficiency, and safety, as well as the ability to align efforts with project timelines and industry standards. These experiences have honed my problem-solving and communication skills, both essential in fulfilling the duties of an IT Assistant.

The responsibilities outlined in the job description align perfectly with my skills and interests. I am eager to learn and practice business communication skills, technology troubleshooting, project management, and computer hardware and software fundamentals. I am also confident in my ability to move or lift up to 35 pounds and my readiness to work both independently and in a team environment.

I am particularly drawn to the learning objectives of this role, as they resonate with my aspirations to continuously grow and contribute positively to the campus technology needs. My attention to detail, self-motivation, positive attitude, and commitment to excellent customer service make me a suitable candidate for this position. My willingness to learn and adapt to new challenges, coupled with my hands-on experience in various technological domains, sets me apart as an IT Assistant.

With a keen interest in aligning my skills with the mission of the LBIS team, I am excited about the opportunity to contribute to Kenyon Faculty, Staff, and academic technologies support. I assure you of my punctual arrival for shifts, consistent attendance, and effective time management.

I would be thrilled to further discuss my qualifications and how they align with the needs of the LBIS team at your convenience. Please find my resume attached for your reference.

Thank you for considering my application. I look forward to the possibility of joining the LBIS team and contributing my skills to Kenyon College.

\closing{Sincerely,}

Richard A. Alvarez \\
+1773 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}
