\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}
\frenchspacing{}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{FuteurAI Hiring Team \\
New York, NY}

\opening{Dear FuteurAI Hiring Team,}

I am writing to express my interest in the Full-Stack AI Technologist position at FuteurAI. My background in programming, data-driven projects, and creative problem-solving equips me to contribute effectively to your AI-driven marketing initiatives. I am eager to apply my skills in Python, API integration, and cloud technologies to build transformative solutions in this space.

During my time at Kenyon College, I worked on several projects at the intersection of AI and creative workflows. For example, I developed a retrieval-augmented recommendation system that combined Node.js and API integration to deliver personalized film suggestions. I also conducted research on video editing trends using unsupervised machine learning techniques and PySceneDetect, demonstrating how AI can uncover patterns in creative industries. These experiences gave me hands-on expertise in Python, scalable workflows, and AI concepts relevant to marketing and engagement.

I have experience managing technical projects independently and delivering results under tight deadlines. As a freelance web developer, I designed and deployed an e-commerce platform using Next.js and TailwindCSS, increasing user engagement by 25\%. I also collaborated on a portfolio site project where I implemented efficient API workflows and ensured smooth user experiences across devices.

What excites me most about this role is the opportunity to work on high-impact, innovative projects at the intersection of AI and marketing. I am particularly drawn to the autonomy and creativity this position offers, as well as the chance to design tools that optimize engagement and streamline processes. I am confident that my technical skills, combined with my ability to work independently, make me a strong candidate for this position.

Thank you for considering my application. I would welcome the opportunity to discuss how my experiences align with the goals of FuteurAI.

Sincerely, \\
Richard Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}

\end{document}