\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{
The Dermot Company \\
New York, NY}

\opening{Dear Hiring Manager,}

I am excited to apply for the Junior IT Technician position at The Dermot Company. With experience in IT support, troubleshooting, and asset management, I am eager to contribute to your team by providing exceptional technical assistance across your properties. My background in helpdesk support and system maintenance has equipped me with the skills necessary to resolve hardware and software issues efficiently while delivering outstanding customer service.

As an IT Assistant at Kenyon College’s Library and Information Services, I provided first-level technical support to faculty, staff, and students. I assisted with troubleshooting computer systems, maintaining office technology, and managing user accounts. Additionally, I developed workflow automation tools to optimize scheduling for maintenance tasks. This experience strengthened my problem-solving abilities and reinforced my commitment to delivering high-quality IT support.

My academic background includes coursework in Data Structures and Program Design, Software Development, and Digital Humanities, providing me with a strong foundation in programming, system administration, and technical troubleshooting. I have also earned the CompTIA ITF+ certification, demonstrating my commitment to professional development in IT.

Key qualifications that align with this role include:
\begin{itemize}
    \item Experience providing first-level IT support, troubleshooting hardware and software issues.
    \item Strong working knowledge of Windows, macOS, and mobile device management.
    \item Familiarity with account setup, lifecycle management, and IT asset tracking.
    \item Excellent communication and customer service skills to support end-users effectively.
    \item Ability to travel between locations and provide on-site IT assistance as needed.
\end{itemize}

I am particularly excited about this opportunity at The Dermot Company because of the role’s combination of hands-on IT support and multi-site operations. I look forward to the opportunity to further discuss how my experience can benefit your IT team.

\closing{Sincerely,}

Richard A. Alvarez \\
+1 (773) 469-9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois (Open to Relocation)

\end{letter}
\end{document}
