\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{Verano Holdings Corp. \\
Chicago, IL 60661}

\opening{Dear Hiring Team,}

I am excited to apply for the Cannabis Advisor position at your West Loop location. As a regular supporter of this store, I’ve always been impressed by the positive atmosphere and the genuine friendliness of your team. Every time I visit, I’m greeted by smiling faces, and the staff is patient and respectful with one another while still delivering excellent customer service. Having met the store manager, I’ve seen firsthand how well the team works together, and I would love to be part of that environment.

Currently, I am focused on paying off student loans and preparing for graduate school, which has taught me the importance of consistency and reliability. These values, combined with my strong work ethic, make me confident that I can be a dependable member of the Verano team. My experience working long hours on film sets in college has prepared me to handle fast-paced, high-energy environments where focus and collaboration are essential.

I am also eager to expand my knowledge of the cannabis industry, especially in the areas of compliance and product education. While I am still learning the technical details of systems like METRC and BioTrack, I understand how critical they are to ensuring the legal and safe distribution of cannabis products. I am committed to learning these tools and adhering to all state and local regulations.

My Latino heritage plays a big role in my desire to give back to my community, and working in a legal, responsible cannabis environment is a way I can contribute meaningfully. I’m excited about the chance to help customers make informed choices, ensuring they have a positive and safe experience at Verano. I believe my enthusiasm for learning, my personal connection to the West Loop location, and my dedication to supporting my community will make me a strong fit for this role.

Thank you for considering my application. I look forward to the opportunity to bring my reliability, positivity, and commitment to learning to your team.

\vspace{1em}

Sincerely, \\ 
Ricky Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}