%-------------------------
% Resume in Latex
% Author : Richard A. Alvarez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome5}
\usepackage{iftex}
\usepackage{fontspec}
\usepackage{xspace} 

% Font configuration
\setmainfont{Avenir}

\frenchspacing 

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable

%-------------------------
% Custom commands

\newcommand{\xsmall}{\fontsize{8pt}{8pt}\selectfont}
\newcommand{\normal}{\fontsize{16pt}{16pt}\selectfont}

\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

% Footer
\fancypagestyle{firstpage}{
  \fancyhf{} % clear all header and footer fields
}

\fancypagestyle{otherpages}{
  \fancyhf{} % clear all header and footer fields
  \fancyfoot[C]{\small Richard Álvarez | 2024}
}

\pagestyle{otherpages}
\thispagestyle{firstpage}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[6]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
        \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\small #2} \\
        \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeParagraph}[1]{
    \item[]
    \parbox{\linewidth}{
        \small{#1\xspace}
    }
    \vspace{-7pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\normal \scshape Richard Álvarez} \\ \vspace{3pt}
    \vspace{12pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:7734699726}{+1 773 469 9726}
    $|$
    \faAt \hspace{.5pt} \href{mailto:rawalvarez731@gmail.com}{rawalvarez731@gmail.com}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/raulduk3}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://raulduke.com}{raulduke.com}
    $|$
    \faMapMarker \hspace{.5pt} Chicago, Illinois
\end{center}

%----------- ABOUT ME  -----------

\section{About Me}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeParagraph{I am an aspiring IT professional with a passion for building community and providing excellent customer service. With years of experience working in dynamic, customer-facing environments, I excel at fostering a welcoming, safe, and educational atmosphere for customers. As a proud Latino, I aim to give back by promoting responsible cannabis use in the growing legal market.}

\vspace{2pt}

\resumeSubHeadingListEnd

\vspace{-12pt}

%----------- EDUCATION -----------

\section{Education}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeEducationHeading
{Kenyon College}{Gambier, Ohio}
{Bachelor of Arts in Film; GPA: 3.47/4.00}{Aug 2020 – May 2024}
{Minor in History; Concentration in Humane Studies}{}
\vspace{-1pt}
\resumeItemListStart
\resumeItem{\textbf{Relevant coursework:} {AI for the Humanities, Programming Humanity, Introduction to Programming, Data Structures \& Program Design}}
\resumeItem{\textbf{Extracurriculars:} {Horn Gallery Videographer, Club Basketball, KSJP}}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Work Experience}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeSubheading
{Library and Information Services (LBIS), Kenyon College}{Gambier, Ohio}
{IT Assistant}{Sep 2023 – Feb 2024}
\resumeParagraph{Prepared and maintained workstations across campus, ensuring technology access for students and staff. Leveraged organizational skills to manage workspaces, streamline classroom tech maintenance, and ensure equipment accuracy for campus events.}

\resumeSubheading
{Fontanos Subs}{Chicago, Illinois}
{Customer Service Specialist}{May 2021 – Aug 2021}
\resumeParagraph{Delivered friendly and efficient service to a wide range of customers, including assisting with complex online orders. Ensured that workstations and public-facing areas were kept clean and organized, fostering a safe and professional environment.}

\resumeSubheading
{Sommerlad Construction}{Chicago, Illinois}
{General Laborer}{Jun 2023 – Aug 2023}
\resumeParagraph{Participated in team efforts to complete renovation projects safely and on time, adhering to compliance standards. Assisted with demolition, general land management, and day-to-day site organization.}

\resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
\textbf{Cannabis Product Expertise:} Familiar with cannabinoids, terpenes, and various product forms (e.g., edibles, tinctures, flower) to guide customer decisions based on wellness needs. \\
\vspace{4pt}

\textbf{Compliance and Regulations:} Knowledgeable in local, state, and federal cannabis laws and safety regulations. \\
\vspace{4pt}

\textbf{Customer Service Excellence:} Skilled at building rapport with diverse customers, providing tailored product recommendations, and fostering repeat business in fast-paced retail environments. \\
\vspace{4pt}

\textbf{Retail Operations:} Adept at maintaining clean, organized workstations; restocking products; merchandising displays; and ensuring compliance with health and safety standards. \\
\vspace{4pt}

\textbf{Bilingual Communication:} Fluent in English and conversational in Spanish, enhancing customer service by assisting Spanish-speaking clients. \\
\vspace{4pt}

\textbf{Technical Skills:} Proficient in Microsoft Office (Word, Excel), email systems, and general office equipment; able to support tech operations in a retail environment.
}}
\resumeSubHeadingListEnd


%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
\vspace{2pt}
\resumeSubHeadingListStart
    \small{\item{
        \textbf{George Washington University Leadership Book Award:}{ Recognized for leadership potential and excellence in academic and community engagement.} \vspace{3pt}
    }}
\resumeSubHeadingListEnd

%———– REFERENCES ———–
%—————————————––
\end{document}
